Title Text

### 2014-04-05 paper.tex
added s to make researcher plural
changes for psi reduction
Some more writing on the introduction of Pull

There are two different ways of implementing Pull arrays in the
literature. The simplest one comes from using Pull arrays in an
embedded langauge, i.e. when the array language is implemented as a
library in another host language. Examples of such languages are
Pan\cite{elliott2003compiling}, Feldspar\cite{Axelsson:2010:Feldspar},
Obsidian\cite{Svensson:2011:Obsidian} and
Nikola\cite{Mainland:2010:Nikola}. By using the technique of
implementing Pull arrays as \emph{shallow embeddings} on top of a
\emph{deeply embedded} code language, fusion comes completely for free
\cite{svenningsson2013combining}.

In the array library Repa\cite{keller2010regular}, compiler supported
rewrite rules are used to implement fusion \cite{jones2001playing}.

@@

@@

>>>>

There are two different ways of implementing Pull arrays in the
literature. The simplest one comes from using Pull arrays in an
embedded langauge, i.e. when the array language is implemented as a
library in another host language. Examples of such languages are
Pan\cite{elliott2003compiling}, Feldspar\cite{Axelsson:2010:Feldspar},
Obsidian\cite{Svensson:2011:Obsidian} and
Nikola\cite{Mainland:2010:Nikola}. By using the technique of
implementing Pull arrays as \emph{shallow embeddings} on top of a
\emph{deeply embedded} code language, fusion comes completely for free
\cite{svenningsson2013combining}.
In the array library Repa\cite{keller2010regular}, compiler supported
rewrite rules are used to implement fusion \cite{jones2001playing}.

Fusion is a powerful optimization which allows programming on a high
level by composing functions without paying an performance penalty.

Fusion effectively makes Pull arrays \emph{virtual} in that they will
not be represented in memory. All intermediate arrays will be
remove. But sometimes it is important to keep an array in memory, not
least to produce the final result. For this reason, Pull arrays
provide a function, variously known as \verb!force!, \verb!memorize!
  or \verb!store!. We will refer to it as \verb!store! here. The
  functional semantics of \verb!store! is the identity function,
  i.e. it simply returns the same array as it was given. However, as a
  side effect it stores the array to memory.

A subtle point about \verb!store! is that the language is still pure
with this function. The reason is that there is no way to observe from
within the language whether an array is stored to memory or
not. Therefore, the side-effect of \verb!store! cannot affect the
value of a computation.

@@

* Only one element type in MoA
* Not much in the way of types in MoA

* Shapes are arrays in MoA whereas they are a different type with Pull arrays

@@

The similarity between MoA and Pull arrays is most clear when
considering Operatonal Normal Form (ONF). Recall that ONF means that
